Automated detection of data fabrication using statistical tools

### 2018-04-26 submission/redraft.rmd
Add paragraph

We tested the performance of statistical methods to detect data fabrication in summary statistics with genuine- and fabricated summary statistics from four anchoring studies [@10.1126/science.185.4157.1124;@10.1037/e722982011-058]. 
The anchoring effect is a well-known psychological heuristic that uses the information in the question as the starting point for the answer, which is then adjusted to yield a final estimate of a quantity. 
For example 'Do you think the percentage of African countries in the UN is above or below  [10\% or 65\%]?  What do you think is the percentage of African countries in the UN?'. 
These questions yield mean responses of 25\% and 45\%, respectively [@10.1126/science.185.4157.1124], despite essentially posing the same factual question. 
A considerable amount of (assumably) genuine data sets on the anchoring  heuristic are freely available [[https://osf.io/pqf9r](https://osf.io/pqf9r); @10.1027/1864-9335/a000178] and we collected fabricated data sets within this study. 
This study was approved by the Tilburg Ethical Review Board (EC-2015.50).

@@

We collected summary statistics for four anchoring studies: (i) distance from San Francisco to New York, (ii) population of Chicago, (iii) height of the Mount Everest, and (iv) the number of babies born per day in the United States [@10.1037/e722982011-058]. 
Each of the four studies provided us with summary statistics for a 2 (low/high anchoring) $\times$ 2 (male/female) factorial design. 
Throughout our study, the unit of analysis is a set of summary statistics (i.e., means, standard deviations, and test results) for the four anchoring studies from one respondent. 
For current purposes, a respondent is defined as researcher/lab where the four anchoring studies' summary statistics originate from. 
All materials, data, and analyses scripts are freely available on the OSF ([https://osf.io/b24pq](https://osf.io/b24pq)) and a preregistration is available at [https://osf.io/tshx8/](https://osf.io/tshx8/). 
Throughout this report, we will indicate which facets were not preregistered or deviate from the preregistration by denoting "(not preregistered)" or "(deviation from preregistration)", respectively.

@@

% We determined which results were most difficult to detect as fabricated using the combined Fisher method, explained further below.

@@

>>>>

We tested the performance of statistical methods to detect data fabrication in summary statistics with genuine- and fabricated summary statistics from four anchoring studies [@10.1126/science.185.4157.1124;@10.1037/e722982011-058]. 
The anchoring effect is a well-known psychological heuristic that uses the information in the question as the starting point for the answer, which is then adjusted to yield a final estimate of a quantity. 
For example 'Do you think the percentage of African countries in the UN is above or below  [10\% or 65\%]?  What do you think is the percentage of African countries in the UN?'. 
These questions yield mean responses of 25\% and 45\%, respectively [@10.1126/science.185.4157.1124], despite essentially posing the same factual question. 
A considerable amount of (assumably) genuine data sets on the anchoring  heuristic are freely available [[https://osf.io/pqf9r](https://osf.io/pqf9r); @10.1027/1864-9335/a000178] and we collected fabricated data sets within this study. 
This study was approved by the Tilburg Ethical Review Board (EC-2015.50).
<!-- link to approval -->

@@

We collected genuine- and fabricated summary statistics for four anchoring studies: (i) distance from San Francisco to New York, (ii) population of Chicago, (iii) height of the Mount Everest, and (iv) the number of babies born per day in the United States [@10.1037/e722982011-058]. 
Each of the four studies provided us with summary statistics for a 2 (low/high anchoring) $\times$ 2 (male/female) factorial design. 
Throughout our study, the unit of analysis is a set of summary statistics (i.e., means, standard deviations, and test results) for the four anchoring studies from one respondent. 
For current purposes, a respondent is defined as researcher/lab where the four anchoring studies' summary statistics originate from. 
All materials, data, and analyses scripts are freely available on the OSF ([https://osf.io/b24pq](https://osf.io/b24pq)) and a preregistration is available at [https://osf.io/tshx8/](https://osf.io/tshx8/). 
Throughout this report, we will indicate which facets were not preregistered or deviate from the preregistration by denoting "(not preregistered)" or "(deviation from preregistration)", respectively.

@@

<!-- % We determined which results were most difficult to detect as fabricated using the combined Fisher method, explained further below.  -->

@@

For each of these statistical tests to detect data fabrication we carried out sensitivity and specificity analyses using Area Under Receiving Operator Characteristic (AUROC) curves. 
AUROC-analyses indicate the sensitivity (i.e., True Positive Rate [TPR]) and specificity (i.e., True Negative Rate [TNR]) for various decision criteria (e.g., $\alpha=0, .01, .02, ..., .99, 1$). 
AUROC values indicate the probability that a randomly drawn fabricated- and genuine dataset can be correctly classified as fabricated and genuine [@10.1148/radiology.143.1.7063747]. 
In other words, if $AUROC=.5$, correctly classifying a randomly drawn dataset as fabricated (or genuine) in this sample is equal to 50%. 
For this setting, we follow the guidelines of @10.1093/jpepsy/jst062 and regard any AUROC value $<.7$ as poor for detecting data fabrication, $.7\leq$ AUROC $<.8$ as fair, $.8\leq$ AUROC $<.9$ as good, and AUROC $\geq.9$ as excellent. 
We conducted these analyses using the `PROC` package [@10.1186/1471-2105-12-77].
